---
title: "Method Comparison"
author: "https://bahar.shinyapps.io/met-comp"
date: "`r Sys.Date()`"
output: html_document
---

#### Assessing aggreement between **`r input$var1`** (reference method) and **`r input$var2`** (test method) measurements by means of Bland-Altman plot:

```{r BA plot, echo=FALSE, results='markup'}
library(mcr)
a <- datasetInput()[,c(input$var1,input$var2), drop=FALSE]
    if (is.null(a)) {
      return(NULL)} else {
        names(a) <- c("M1", "M2")
        data1 <- mcreg(a$M1, a$M2,
                      mref.name = input$var1, mtest.name = input$var2)
        MCResult.plotDifference(data1, plot.type = input$batype, add.grid = TRUE)
      }
```

___

#### Scatter plot of **`r input$var1`** (reference method) and **`r input$var2`** (test method) measurements:

```{r regression plot, echo=FALSE, results='markup'}
library(mcr)
a <- datasetInput()[,c(input$var1,input$var2), drop=FALSE]
    if (is.null(a)) {
      return(NULL)} else {
        names(a) <- c("M1", "M2")
        data1<- mcreg(a$M1,a$M2, error.ratio = input$syx, 
                      method.reg = input$regmodel, method.ci = input$cimethod,
                      method.bootstrap.ci = input$metbootci)
        MCResult.plot(data1, ci.area=input$ciarea, 
             add.legend=input$legend, identity=input$identity,
             add.cor=input$addcor, x.lab=input$var1,
             y.lab=input$var2, cor.method=input$cormet, 
             equal.axis = TRUE, add.grid = TRUE)
      }
```

___

#### Regression analysis summary:

```{r statistics, echo=FALSE, comment = '', warning = FALSE, message = FALSE}
library(mcr)
library(pander)
a <- datasetInput()[,c(input$var1,input$var2), drop=FALSE]
    if (is.null(a)) {
      return(NULL)} else {
        names(a) <- c("M1", "M2")
        data1 <- mcreg(a$M1, a$M2, error.ratio = input$syx, 
                      method.reg = input$regmodel, method.ci = input$cimethod,
                      method.bootstrap.ci = input$metbootci,
                      mref.name = input$var1, mtest.name = input$var2)
        pander(getCoefficients(data1))
      }
```

___

#### Data is processed using R language^1^, shiny web application framework^2^ and mcr package^3^.

##### References:

1. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
  
2. shiny: Web Application Framework for R. R package version 0.12.2. URL http://CRAN.R-project.org/package=shiny

3. mcr: Method Comparison Regression. R package version 1.2.1. URL http://CRAN.R-project.org/package=mcr